```{r}
# Load the dataset
dataset <- read.csv("games_fixed_columns.csv")

require(evd)
library(evd)

require(MASS)
library(MASS)

require(fitdistrplus)
library(fitdistrplus)

require(VGAM)
library(VGAM)

require(stats)
library(stats)

```

```{r}
# install.packages("fitdistrplus")
# install.packages("MASS")
# install.packages("actuar")


```

($H_0$): The prices in the dataset follow an exponential distribution with rate parameter $\lambda = \frac{1}{\text{mean_price}}$. $$
    H_0: F(x) = 1 - e^{-\lambda x}, \quad \text{for } x \geq 0
    $$

($H_1$): The prices in the dataset do not follow an exponential distribution with rate parameter $\lambda = \frac{1}{\text{mean_price}}$. $$
    H_1: F(x) \neq 1 - e^{-\lambda x}, \quad \text{for } x \geq 0
    $$

```{r}
mean_price <- mean(dataset$Price, na.rm = TRUE)
lambda <- 1 / mean_price  # Exponential rate parameter

# Plot the histogram of the original data
breaks <- c(seq(0, 49.5, by = 0.5), Inf)
hist_obj <- hist(dataset$Price,
                 breaks = breaks,
                 main = "Price Distribution with Exponential Fit",
                 xlab = "Price Ranges",
                 ylab = "Count of Prices",
                 col = "skyblue",
                 border = "white",
                 freq = FALSE,   # Y-axis shows density
                 xlim = c(0, 51))

# Add the theoretical exponential density curve
curve(dexp(x, rate = lambda), 
      col = "red", 
      lwd = 2, 
      add = TRUE)

# Perform Kolmogorov-Smirnov test to assess goodness of fit
ks_test <- ks.test(dataset$Price, "pexp", rate = lambda)
print(ks_test)

# Add legend
legend("topright", legend = c("Original Data", "Exponential Fit"), 
       col = c("skyblue", "red"), 
       lwd = 2, 
       bty = "n")


```

We reject $H_0$ in favor of the alternative hypothesis $H_1$. This tells us that the price distribution does not follow an exponential distribution and we cannot tell, which distribution it is.

```{r}

sum_values <- dataset$Positive + dataset$Negative

difference <- ifelse(
  sum_values > 100,
  dataset$Positive + 1 / (dataset$Negative + dataset$Positive + 2),
  NA
)

difference <- difference[difference <= 1000 & !is.na(difference)]


breaks <- seq(floor(min(difference)), ceiling(max(difference)), by = 1)

hist(
  difference,
  breaks = breaks,
  main = "Normalized value of user score (Filtered and Limited to 1000)",
  xlab = "Relation of positive to overall score",
  col = "lightblue",
  border = "blue",
  freq = TRUE, 
  xlim = c(min(breaks), max(breaks))
)



```

```{r}
# Load required libraries



fit_normal <- fitdistr(difference, "normal")

fit_exponential <- fitdistr(difference, "exponential")

fit_weibull <- fitdistr(difference, "weibull")


fit_genextreme <- vglm(difference ~ 1, gev, trace = FALSE)

hist(
  difference,
  breaks = breaks,
  freq = FALSE,
  main = "Histogram with Fitted Distributions",
  xlab = "Difference",
  col = "lightblue",
  border = "blue"
)

curve(
  dnorm(x, mean = fit_normal$estimate["mean"], sd = fit_normal$estimate["sd"]),
  col = "red",
  lwd = 2,
  add = TRUE
)

curve(
  dexp(x, rate = fit_exponential$estimate["rate"]),
  col = "black",
  lwd = 2,
  add = TRUE
)

curve(
  dweibull(x, shape = fit_weibull$estimate["shape"], scale = fit_weibull$estimate["scale"]),
  col = "green",
  lwd = 2,
  add = TRUE
)

curve(
  dgev(
    x, 
    loc = Coef(fit_genextreme)["location"], 
    scale = Coef(fit_genextreme)["scale"], 
    shape = Coef(fit_genextreme)["shape"]
  ),
  col = "orange",
  lwd = 2,
  add = TRUE
)


legend(
  "topright",
  legend = c("Normal", "Exponential", "Weibull", "GEV"),
  col = c("red", "black", "green", "orange"),
  lwd = 2
)


```

```{r}
# Load required library

# Empirical distribution
empirical <- ecdf(difference)

# P-value calculations

# Normal distribution
ks_normal <- ks.test(
  difference,
  "pnorm",
  mean = fit_normal$estimate["mean"],
  sd = fit_normal$estimate["sd"]
)

# Exponential distribution
ks_exponential <- ks.test(
  difference,
  "pexp",
  rate = fit_exponential$estimate["rate"]
)

# Weibull distribution
ks_weibull <- ks.test(
  difference,
  "pweibull",
  shape = fit_weibull$estimate["shape"],
  scale = fit_weibull$estimate["scale"]
)

# Generalized Extreme Value (GEV) distribution
ks_genextreme <- ks.test(
  difference,
  "pgev",
  loc = Coef(fit_genextreme)["location"],
  scale = Coef(fit_genextreme)["scale"],
  shape = Coef(fit_genextreme)["shape"]
)

# Extract p-values
p_values <- c(
  normal = ks_normal$p.value,
  exponential = ks_exponential$p.value,
  weibull = ks_weibull$p.value,
  genextreme = ks_genextreme$p.value
)

# Find the distribution with the largest p-value
best_fit <- names(which.max(p_values))
largest_p_value <- max(p_values)

# Print results
print("P-values for each distribution:")
print(p_values)
cat("Distribution with the largest p-value:", best_fit, "\n")
cat("Largest p-value:", largest_p_value, "\n")


```

The closest distribution is genextreme (<https://en.wikipedia.org/wiki/Generalized_extreme_value_distribution>). But we can not say that this is the distribution of our distribution of scores, because of small p-value.
