---
title: "P&S-2024: Final Project"
author: |
  Viktor Pakholok (<https://github.com/viktorpakholok>)  
  Lysyk Lev (<https://github.com/Lius912>)  
  Bohdan Milian (<https://github.com/Bohdanok>)
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: 60
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
require(evd)
library(evd)

require(MASS)
library(MASS)

require(fitdistrplus)
library(fitdistrplus)

require(VGAM)
library(VGAM)

require(stats)
library(stats)

require(ggplot2)
library(ggplot2)

require(reshape2)
library(reshape2)

require(DT)
library(DT)

```

# **The aim of the project:**

Analyze and visualize the dataset provided by the Steam game service to identify and explore potential correlations between various characteristics. Get some meaningful insights and present them.

## *For this we used the dataset from Kaggle*

<https://www.kaggle.com/datasets/fronkongames/steam-games-dataset?resource=download>

# **Data specifications:**

*This dataset provides detailed information about video games, including their titles, release dates, pricing, and supported platforms (Windows, Mac, Linux). It has user interaction metrics like peak concurrent users, reviews, and playtime data, along with additional details such as categories, genres, tags, and achievements. The dataset also captures commercial and content-related information like estimated owners, downloadable content (DLC) counts, and Metacritic scores for popular games.*

```{r, warning=FALSE, message=FALSE}
dataset <- read.csv("games_fixed_columns2.csv")
head(dataset, 7)
```

($H_0$): The prices in the dataset follow an exponential distribution
with rate parameter $\lambda = \frac{1}{\text{mean_price}}$. $$
    H_0: F(x) = 1 - e^{-\lambda x}, \quad \text{for } x \geq 0
    $$

($H_1$): The prices in the dataset do not follow an exponential
distribution with rate parameter
$\lambda = \frac{1}{\text{mean_price}}$. $$
    H_1: F(x) \neq 1 - e^{-\lambda x}, \quad \text{for } x \geq 0
    $$

```{r}
mean_price <- mean(dataset$Price, na.rm = TRUE)
lambda <- 1 / mean_price

breaks <- c(seq(0, 49.5, by = 1), Inf)
hist_obj <- hist(dataset$Price,
                 breaks = breaks,
                 main = "Price Distribution with Exponential Fit",
                 xlab = "Price Ranges",
                 ylab = "Count of Prices",
                 col = "skyblue",
                 border = "blue",
                 freq = FALSE,
                 xlim = c(0, 51))

curve(dexp(x, rate = lambda), col = "red", lwd = 2, add = TRUE)

ks_test <- ks.test(dataset$Price, "pexp", rate = lambda)
print(ks_test)

legend("topright", legend = c("Original Data", "Exponential Fit"), 
       col = c("skyblue", "red"), 
       lwd = 2, 
       bty = "n")


```

We reject $H_0$ in favor of the alternative hypothesis $H_1$. This tells
us that the price distribution does not follow an exponential
distribution and we cannot tell, which distribution it is.



Now we will try to plot the distribution of scores, that users gave to
the games. Since our dataset provides the count of positive and negative
scores, we will try to normalize them in the way:
$$Score = \frac{Positive + 1}{\text{Positive + Negative + 2}}$$ to plot
them in a compatible way.

```{r}
sum_values <- dataset$Positive + dataset$Negative
difference <- ifelse(sum_values > 45, (dataset$Positive + 1) / (dataset$Negative + dataset$Positive + 2),NA)

difference <- difference[!is.na(difference)]

breaks <- seq(floor(min(difference)), ceiling(max(difference)), length.out = 100)

hist(
  difference,
  breaks = breaks,
  main = "Normalized value of user score (Filtered)",
  xlab = "Relation of positive to overall score",
  col = "lightblue",
  border = "blue",
  freq = FALSE,
  xlim = range(0, 1.05)
)

```


```{r}

fit_normal <- fitdistr(difference, "normal")

fit_exponential <- fitdistr(difference, "exponential")

fit_weibull <- fitdistr(difference, "weibull")


fit_genextreme <- vglm(difference ~ 1, gev, trace = FALSE)

hist(
  difference,
  breaks = breaks,
  freq = FALSE,
  xlim = range(0, 1.05),
  main = "Histogram with Fitted Distributions",
  xlab = "Difference",
  col = "lightblue",
  border = "blue"
)

curve(dnorm(x, mean = fit_normal$estimate["mean"], sd = fit_normal$estimate["sd"]), col = "red", lwd = 2, add = TRUE)

curve(dexp(x, rate = fit_exponential$estimate["rate"]), col = "black", lwd = 2, add = TRUE)

curve(dweibull(x, shape = fit_weibull$estimate["shape"], scale = fit_weibull$estimate["scale"]), col = "green", lwd = 2, add = TRUE)

curve(dgev(x, loc = Coef(fit_genextreme)["location"], scale = Coef(fit_genextreme)["scale"], shape = Coef(fit_genextreme)["shape"]), col = "orange", lwd = 2, add = TRUE)


legend(
  "topleft",
  legend = c("Normal", "Exponential", "Weibull", "GEV"),
  col = c("red", "black", "green", "orange"),
  lwd = 2
)

```


```{r}
empirical <- ecdf(difference)

# Normal distribution
ks_normal <- ks.test(
  difference,
  "pnorm",
  mean = fit_normal$estimate["mean"],
  sd = fit_normal$estimate["sd"]
)

# Exponential distribution
ks_exponential <- ks.test(
  difference,
  "pexp",
  rate = fit_exponential$estimate["rate"]
)

# Weibull distribution
ks_weibull <- ks.test(
  difference,
  "pweibull",
  shape = fit_weibull$estimate["shape"],
  scale = fit_weibull$estimate["scale"]
)

# Generalized Extreme Value (GEV) distribution
ks_genextreme <- ks.test(
  difference,
  "pgev",
  loc = Coef(fit_genextreme)["location"],
  scale = Coef(fit_genextreme)["scale"],
  shape = Coef(fit_genextreme)["shape"]
)

p_values <- c(
  normal = ks_normal$p.value,
  exponential = ks_exponential$p.value,
  weibull = ks_weibull$p.value,
  genextreme = ks_genextreme$p.value
)

best_fit <- names(which.max(p_values))
largest_p_value <- max(p_values)

print("P-values for each distribution:")
print(p_values)
cat("Distribution with the largest p-value:", best_fit, "\n")
cat("Largest p-value:", largest_p_value, "\n")
```

The closest distribution is genextreme
(<https://en.wikipedia.org/wiki/Generalized_extreme_value_distribution>).
But we can not say that this is the distribution of our distribution of
scores, because of small $p-value$.

```{r}

dataset$normalizedScore <- ((dataset$Positive + 1) / (dataset$Negative + dataset$Positive + 2))

filtered_dataset <- dataset[dataset$Metacritic.score > 0, ]

correlation_matrix <- cor(filtered_dataset[sapply(filtered_dataset, is.numeric) & names(filtered_dataset) != "Score.rank" & names(filtered_dataset) != "Positive" & names(filtered_dataset) != "Negative" &names(filtered_dataset) != "X"])


ggplot(data = melt(correlation_matrix), aes(x = Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +

  geom_text(aes(label = sprintf("%.2f", value)), color = "black", size = 3) +

  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0,
                       limit = c(-1, 1), space = "Lab", name = "Correlation") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank()
  ) +
  ggtitle("Correlation Heatmap to see the relation between different values of the dataset") +
  theme(plot.title = element_text(hjust = 0.5))

```

From this heatmap we can see, that the correlation between the
Metacritic score (<https://www.metacritic.com/>) and user score is
considerable, although not very high. This is because the point of view
of professionals not always aligns with the masses.
