```{r}
games_data <- read.csv("games_fixed_columns.csv")
```

```{r}
games_data[["Reviews count"]] <- (games_data[["Positive"]] + games_data[["Negative"]])
games_data[["Rating"]] <- games_data[["Positive"]] / (games_data[["Reviews count"]])

data_with_reviews <- function(cur_data, min_reviews_count) {
  return (games_data[games_data[["Reviews count"]] > min_reviews_count, ])
}

```

```{r}

get_year <- function(date) {
  date_length <- nchar(date)
  return (substr(date, date_length - 3, date_length))
  
}

get_all_years <- function(cur_data) {
  years <- new.env()
  for (date in cur_data[, "Release.date"]) {
    years[[get_year(date)]] = 0
  }
  for (year in ls(years)) {
    assign(year, new.env(), envir = years)
  }
  return (years)
}
```

```{r}

select_top_genre <- function(years) {
  top_genres_by_year <- list()
  for (year in ls(years)) {
    genres_count <- years[[year]]
    most_popular_genre <- ""
    max_count <- -1
    for (genre in ls(genres_count)) {
      count <- genres_count[[genre]]
      if (count > max_count && genre != "Sexual Content" && genre != "Nudity") {
        max_count = count
        most_popular_genre <- genre
      }
    }
    top_genres_by_year[[paste(most_popular_genre, ": ", year, sep = "")]] = max_count
  }
  return (top_genres_by_year)
}
count_genres_by_years <- function(cur_data) {
  years <- get_all_years(cur_data)

  for (i in 1:nrow(cur_data)) {
    date <- cur_data[i, "Release.date"]
    year <- get_year(date)
    genres <- cur_data[i, "Genres"]
    genres_vec <- unlist(strsplit(genres, ","))
    cur_year_genres_count <- years[[year]]
    for (genre in genres_vec) {
      if (!exists(genre, envir = cur_year_genres_count)) {
        cur_year_genres_count[[genre]] <- 0
      }
      cur_year_genres_count[[genre]] <- cur_year_genres_count[[genre]] + 1
    }
  }
  return (years)
}

sum_genres_rating_by_years <- function(cur_data) {
  years <- get_all_years(cur_data)

  for (i in 1:nrow(cur_data)) {
    date <- cur_data[i, "Release.date"]
    year <- get_year(date)
    
    genres <- cur_data[i, "Genres"]
    genres_vec <- unlist(strsplit(genres, ","))
    
    rating <- cur_data[i, "Rating"]
    cur_year_genres_sum_rating <- years[[year]]
    for (genre in genres_vec) {
      if (!exists(genre, envir = cur_year_genres_sum_rating)) {
        cur_year_genres_sum_rating[[genre]] <- 0
      }
      cur_year_genres_sum_rating[[genre]] <- cur_year_genres_sum_rating[[genre]] + rating
    }
  }
  return (years)
}

average_genres_rating_by_years <- function(cur_data, count_by_years, sum_rating_by_years) {
  average_rating_by_years <- get_all_years(cur_data)

  for (year in ls(sum_rating_by_years)) {
    for (genre in ls(sum_rating_by_years[[year]])) {
      average_rating_by_years[[year]][[genre]] <- sum_rating_by_years[[year]][[genre]] / count_by_years[[year]][[genre]]
    }
  }
  return (average_rating_by_years)
}



get_most_created_genre_by_years <- function(cur_data) {
  years <- count_genres_by_years(cur_data)
  return (select_top_genre(years))
}

get_most_rated_genre_by_years <- function(cur_data) {
  sum_rating <- sum_genres_rating_by_years(cur_data)
  years <- average_genres_rating_by_years(cur_data, count_genres_by_years(cur_data), sum_rating)
  return (select_top_genre(years))
}

```

```{r}
min_reviews_count <- 5
games_data2 <- data_with_reviews(games_data, min_reviews_count)

top_genre_by_years <- unlist(get_most_created_genre_by_years(games_data2))

par(mar = c(5,8, 2, 1))
blue_shades <- adjustcolor(rainbow(length(top_genre_by_years), start=.5, end=.65), alpha.f = 0.7)
barplot(unlist(top_genre_by_years), main = "The most popular genre by years", xlab="Games count",
        las=1, col=blue_shades,
        horiz = TRUE, cex.names = 0.6, xlim=c(0, max(top_genre_by_years))
        )
```

Looking at the graph above we can see that most games from 1997 to 2012 are **action**.

In 2005 and 2006 RPG and **strategy** were created the most which is because more people liked these games, so more games of these genres were produced.

And in years from 2013 to 2024 **indie** games were the most popular because game development became easier, more guides were available on the internet so more games were created by small teams consisting of several developers.

```{r}
min_reviews_count <- 100
games_with_reviews <- data_with_reviews(games_data, min_reviews_count)
top_rated_genre_by_years <- get_most_rated_genre_by_years(games_with_reviews)
par(mar = c(5,8, 2, 1))
blue_shades <- adjustcolor(rainbow(length(top_rated_genre_by_years), start=.5, end=.65), alpha.f = 0.7)
barplot(unlist(top_rated_genre_by_years) * 10,
              main = paste("The most rated genres by years(reviews count > ", min_reviews_count, ")"),
              xlab="Average user rating", las=1, col=blue_shades,
              horiz = TRUE, cex.names = 0.6, xlim=c(0, 10)
              )

```

This barplot depicts that from 1997 to 2006 generally **action** genre was the most rated.

Then plot shows that **free to play** games became well rated because this is probably the time when more free games started coming out.

Steam is targetted as platform for games, but it still has other applications and from 2012 most rated games are not actually games, but rather applications for **modeling**, **animating** and even **game development** in 2021.
